Projektplan

### 2021-03-12 documentation/projektplan/problemformulering.tex
Updates from Overleaf

\section{Activity Plan}
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{documentation/images/projectPlan.pdf}
    \caption{The project activity plan}
    \label{fig:my_label}
\end{figure}
\subsection*{Meetings}
We will have a weekly meeting with both the project coordinator Christian Kampp Kruuse and our supervisor Martin Schoeberl on Fridays. In addition, meetings will be arranged with our second supervisor Vitaliy Zhurbenko if necessary. 
\subsection*{Report writing}
We will begin drafting a project report once we have achieved an MVP (Minimum Viable Product). The report will include full documentation of all design choices in hardware and software. 
\subsection*{Design}
The design phase of the project will include designing prototypes to be implemented once the hardware components become available. Furthermore, basic software programs may be written and debugged during the design phase. We intend for all design, prototyping and testing of the Solar Car Unit (SC) and Support Vehicle Unit (SV) to run in parallel. 
\subsection*{Prototyping}
During prototyping we want to test the basic functionality of our product. The setup should be configurable, which is why we plan to use breadboards and jumper wires. Basic tests will be written in software to make sure the product meets the basic requirements. 
\subsection*{Requirements fulfilled}
Once the basic requirements have been fulfilled by the prototype we will begin rigorously testing to find ways to further optimise our design. This is to ensure that the product will not have any fundamental flaws. 
\subsection*{Product Development}
This stage will concern the design of an MVP as well as later design iterations. 
\subsection*{GUI}
As a final touch we intend to create a basic GUI allowing PC users to interact with the telemetry module, as well as sending and receiving data on the CAN bus. 
\subsection*{Field Testing and Validation}
Finally, our product will be integrated with the ROAST solar car and support vehicle, allowing us to test it in operation. We will be able to gain feedback from the DTU ROAST team and evaluate the project. 
\newpage
\section{System Specification}

@@

\section{References}
\begingroup
\renewcommand{\section}[2]{}%
%\renewcommand{\chapter}[2]{}% for other classes
\begin{thebibliography}{}
\bibitem{wsc}
Bridgestone World Solar Challenge, 
URL: https://worldsolarchallenge.org/
\bibitem{ROAST}
Reports and source files provided by DTU ROAST
\bibitem{teensy}
Teensy microcontroller,
URL: https://www.pjrc.com/teensy/
\end{thebibliography}
\endgroup

>>>>

\section{Activity Plan}
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{documentation/images/projectPlan.pdf}
    \caption{The project activity plan}
    \label{fig:my_label}
\end{figure}
\subsection*{Meetings}
We will have a weekly meeting with both the project coordinator Christian Kampp Kruuse and our supervisor Martin Schoeberl on Fridays. In addition, meetings will be arranged with our second supervisor Vitaliy Zhurbenko if necessary. 
\subsection*{Paper writing}
We will begin drafting a project paper once we have achieved an MVP (Minimum Viable Product). A Github repository will be updated continuously as a full documentation of the project.
\subsection*{Design}
The design phase of the project will include designing prototypes to be implemented once the hardware components become available. Furthermore, basic software programs may be written and debugged during the design phase. We intend for all design, prototyping and testing of the Solar Car Unit (SC) and Support Vehicle Unit (SV) to run in parallel. 
\subsection*{Prototyping}
During prototyping we want to test the basic functionality of our product. The setup should be configurable, which is why we plan to use breadboards and jumper wires. Basic tests will be written in software to make sure the product meets the basic requirements. 
\subsection*{Requirements fulfilled}
Once the basic requirements have been fulfilled by the prototype we will begin rigorously testing to find ways to further optimise our design. This is to ensure that the product will not have any fundamental flaws. 
\subsection*{Product Development}
This stage will concern the design of an MVP as well as later design iterations. 
\subsection*{GUI}
As a final touch we intend to create a basic GUI allowing PC users to interact with the telemetry module, as well as sending and receiving data on the CAN bus. 
\subsection*{Field Testing and Validation}
Finally, our product will be integrated with the ROAST solar car and support vehicle, allowing us to test it in operation. We will be able to gain feedback from the DTU ROAST team and evaluate the project. 
\newpage
\section{System Specification}

@@

\section{References}
\begingroup
\renewcommand{\section}[2]{}%
%\renewcommand{\chapter}[2]{}% for other classes
\begin{thebibliography}{}
\bibitem{wsc}
Bridgestone World Solar Challenge, 
URL: https://worldsolarchallenge.org/
\bibitem{ROAST}
Reports and source files provided by DTU ROAST
\bibitem{teensy}
Teensy microcontroller,
URL: https://www.pjrc.com/teensy/
\bibitem{C++}
Website for learning C++
https://www.learn-cpp.org/
\end{thebibliography}
\endgroup
